

%\fi
%%%%%%%%%
%% Conclusion
\section{Conclusion}

In this paper we present our work on using the POWDER mobile and wireless
research platform to conduct RF propagation related research. We showed
how ground truth RF measurements obtained from the POWDER platform can
be compared with an RF propagation prediction tool. 
Specifically, we performed measurements using the Shout measurement framework
and compared the resulting data with predicted power levels obtained from the
SPLAT! RF propagation tool. 

While useful in its own right to inform our efforts as we continue 
to build out the POWDER platform, the primary aim of our work is to
illustrate the utility of POWDER to enable this type of research. To that end,
we have packaged our work into a POWDER profile that enables others to
replicate our results and to serve as a starting point for related research
efforts~\cite{paper_profile}. 

\iffalse
In this paper we discussed RF propagation. Specifically, we covered RF propagation models, ran a few measurements on the 
POWDER platform, discussed our results, and compared the data between our propagation model and the ``ground truth". 
SPLAT! was our RF propagation model of choice and its measurement results were compared with the Shout framework. Shout 
was developed by the POWDER team to conduct measurement studies on the POWDER platform. 

Our results showed that SPLAT! on the 3561 MHz and 2620 MHz frequencies overpredicted the path loss, however on the 3550 
MHz and 3690 MHz SPLAT! under-predicted the path loss with respect to the Shout framework. Furthermore, on the 3561 MHz
frequency, Shout and SPLAT! both picked the same two nodes with the best RF propagation, but failed to choose the same two 
nodes when it came to picking nodes with the worst RF propagation. There is no definitive answer as to whether or not Shout 
has been validated with respect to SPLAT!. RF propagation models take into account multiple parameters to calculate path loss,
it could just so be that SPLAT! is not the ideal model for the POWDER platform.
\fi
